rang: Reconstructing reproducible R computational environments with ease

### 2023-02-16 paper/paper.rmd
Add hilgard

@cruewell:2023:WB evaluate the computational reproducibility of 14 articles published in **Psyhocological Science**. Among these articles, the paper by @hilgard:2019:NEG has been rated as having "package dependency issues".

All data and computer code are available from Github with the last commit on 2019-01-17. The R code contains a list of R packages used in the project, included an R package on Github that is written by the main author of that paper.

Based on the shared, one can run `rang` to obtain the dependecy graph of all R packages on 2019-01-17.

```r
graph <- resolve(c("readxl", "rms", "ordinal", "tidyverse", "lubridate", "MBESS", "censReg",
                   "BayesFactor", "psych", "Joe-Hilgard/hilgard", "lsmeans"),
                 snapshot_date = "2019-01-17")
```

>>>>

 @cruewell:2023:WB evaluate the computational reproducibility of 14 articles published in *Psyhocological Science*. Among these articles, the paper by @hilgard:2019:NEG has been rated as having "package dependency issues".

All data and computer code are available from Github with the last commit on 2019-01-17 [^hilgard]. The R code contains a list of R packages used in the project as `library()` statements, included an R package on Github that is written by the main author of that paper. However, we identified one package (`compute.es`) that was not written in those `library()` statements but used with the namespace operator, i.e. `compute.es::tes()`. This undocumented package can be detected by `renv::dependencies()`.

[^hilgard]: https://github.com/Joe-Hilgard/vvg-2d4d

Based on the above information, one can run `resolve()` to obtain the dependency graph of all R packages on 2019-01-17.

```r
graph <- resolve(c("readxl", "rms", "ordinal", "tidyverse", "lubridate", "MBESS",
                   "censReg", "BayesFactor", "psych", "Joe-Hilgard/hilgard", "lsmeans",
                   "compute.es"),
                 snapshot_date = "2019-01-17")
```

When running `dockerize()`, one can take advantage of the `materials_dir` parameter to transfer the shared materials from @hilgard:2019:NEG into the Docker image.

```r
dockerize(graph, "hilgard", materials_dir = "vvg-2d4d", cache = TRUE)
```

We then built the Docker and launch a Docker container. For this container, we changed the entry point from R to bash so that the container goes to the Linux command shell instead.

```r
cd hilgard
docker build -t hilgard .
docker run --rm --name "hilgardcontainer" --entrypoint bash -ti hilgard
```

Inside the container, the materials is located in the `materials` directory. We used the following shell script to test the reproducibility of all R scripts.

```sh
rfiles=(0_data_aggregation.R 1_data_cleaning.R 2_analysis.R 3_plotting.R)
for i in ${rfiles[@]}
do
	Rscript $i
	code=$?
	if [ $code != 0 ]
	then
		exit 1
	fi
done   
```

All R scripts ran fine inside the container and the figures generated are the same as the ones in @hilgard:2019:NEG.
